The imprint of global magma oceans on exoplanet demographics

### 2023-03-08 src/tex/ms.tex
discuss the value of follow-up campaigns

\subsubsection{The value of follow-up campaigns}
\begin{note}
As runaway greenhouse phases leave a stronger imprint in bulk density than in planet radius (see Sect.~\ref{sec:res_followup}), it would be beneficial to obtain constraints on planetary masses and test the runaway greenhouse hypothesis in density space instead of radius space.
Precise ground-based radial velocity measurements are expensive, and therefore such follow-up efforts may only be available for a subsample of a mission's targets.
For a mission design similar to PLATO, a density-based test on about a third of the overall sample is equivalent to a pure radius-based analysis.
The diagnostic power of such a test may be improved by simultaneously fitting for the trend in radius space in the subsample without RV follow-up.
An optimized mission in search for the inner edge of the habitable zone will further enhance its information content via a wise selection of follow-up targets, i.e., favoring those planets residing close to the expected instellation threshold $S_\mathrm{thresh}$.
\end{note}

@@

\subsection{Impact of assumptions on our findings}
\todo[inline]{Caveats\\
context: \citet{Turbet2019} Sect. 3, \citet{Bower2019}.\\
''present bracketing cases; or to discuss why the discountinuity in the results would not be affected by changes that led to continuous offsets in the results. Or both.''}
\subsubsection{Baseline mass-radius relationship}
Our baseline mass-radius relationship assuming pure $\mathrm{MgSiO_3}$ interiors~\citep{Zeng2016} might not be representative of the rocky planet population.
However, while interior composition may change the magnitude of radius inflation and could introduce an offset to its demographic imprint, we do not expect a change of its structure.
The magnitude of the radius inflation effect is in fact expected to be larger for an Earth-like interior composition with an iron core-silicate mantle structure.\todo[inline]{TIM: do you have a reference for this statement?}
We thus consider our mass-radius relationship a conservative case and do not expect a negative impact on the detectability of the runaway greenhouse transition due to deviations from it.
\todo[inline]{if feasible: run a test with a different M-R relation. do we expect that the choice of M-R relation impacts the results? Perhaps have an appendix section.}

>>>>

\subsubsection{The value of follow-up campaigns}
As runaway greenhouse phases leave a stronger imprint in bulk density than in planet radius (see Sect.~\ref{sec:res_followup}), it would be beneficial to obtain constraints on planetary masses and test the runaway greenhouse hypothesis in density space instead of radius space.
This way, useful constraints can be obtained under more pessimistic conditions, e.g., a low predominant water content of planetary surfaces and atmospheres or a smaller available planet sample.
For a mission design similar to PLATO, a density-based hypothesis test on about a third of the overall sample is equivalent to a pure radius-based analysis.
At a fixed sample size, key parameters of the runaway greenhouse models can be more narrowly constrained when additional mass measurements are available.

However, precise ground-based radial velocity measurements are expensive, and therefore such follow-up efforts may only be available for a subsample of a mission's targets.
The diagnostic power of such a test may be improved by simultaneously fitting for the trend in radius space in the subsample without RV follow-up.
An optimized mission in search for the inner edge of the habitable zone will further enhance its information content via a wise selection of follow-up targets, i.e., favoring those planets residing close to the expected instellation threshold $S_\mathrm{thresh}$.

@@

\subsection{Impact of assumptions on our findings}
\todo[inline]{Caveats\\
context: \citet{Turbet2019} Sect. 3, \citet{Bower2019}.\\
''present bracketing cases; or to discuss why the discountinuity in the results would not be affected by changes that led to continuous offsets in the results. Or both.''\\
- not yet explored: how sensitive are we on the assumed planet population? $\exists$ danger of false positive detection on occurrence rate ``ridges'' like the Neptune desert? Currently we have a relatively smooth occurrence rate density in $R_P - S$ space based on the power-law fits in \citet{Bergsten2022}. We could, with relatively moderate effort, run a sanity check on an alternative sample (e.g., the more structured Bern model)}
\subsubsection{Baseline mass-radius relationship}
Our baseline mass-radius relationship assuming pure $\mathrm{MgSiO_3}$ interiors~\citep{Zeng2016} might not be representative of the rocky planet population.
However, while interior composition may change the magnitude of radius inflation and could introduce an offset to its demographic imprint, we do not expect a change of its structure.
The magnitude of the radius inflation effect is in fact expected to be larger for an Earth-like interior composition with an iron core-silicate mantle structure.\todo[inline]{TIM: do you have a reference for this statement?}
We thus consider our mass-radius relationship a conservative case and do not expect a negative impact on the detectability of the runaway greenhouse transition due to deviations from it.
\todo[inline]{if feasible: run a test with a different M-R relation. do we expect that the choice of M-R relation impacts the results? Perhaps have an appendix section.}
